COG-ED Manuscript

### 2022-01-11 06_Paper/COG-ED/Manuscript.Rmd
started writing graph code for SCA

  knitr::opts_chunk$set(echo = TRUE)
  library(bibtex)
  library(here)         # to set a directory without defined paths, "here" package
  library(tidyverse)    # plotting and managing data, "tidyverse" package
  library(bayestestR)   # computing area under the curve, "bayestestR" package
  library(papaja)       # APA conform output, "papaja" package
  library(lmerTest)     # for multilevel modeling
  library(afex)         # compute repeated measures ANOVA, "afex" package
  library(emmeans)      # for custom contrasts in ANOVAs, "emmeans" package
  library(sjPlot)       # plot MLM model fit
  library(kableExtra)   # for great tables in R Markdown
  library(interactions) # for simple slopes analysis
  library(huxtable)     # create huxtable
  library(glmmTMB)      # from the glmmTMB package for multi level models
  library(BayesFactor)  # computing Bayes factors, "BayesFactor" package

@@

  sca_results <- data.frame(pipeline = character(), beta_level = double(), p_level = double(),
                            beta_nfc = double(), p_nfc = double())

@@

    newdata <- data.frame(pipeline = names(pipelines_data[i]),
                          beta_level = summary(m1_sca)$coefficients[2,1],
                          p_level = summary(m1_sca)$coefficients[2,5],
                          beta_nfc = summary(m1_sca)$coefficients[3,1],
                          p_nfc = summary(m1_sca)$coefficients[3,5])
    sca_results <- rbind(sca_results, newdata)

@@

  # sort the data frame by the fixed effects estimate of the predictor 'level'

  sca_results <- sca_results[order(beta_level), ]

>>>>

  knitr::opts_chunk$set(echo = TRUE)
  library(bibtex)
  library(here)         # to set a directory without defined paths, "here" package
  library(tidyverse)    # plotting and managing data, "tidyverse" package
  library(bayestestR)   # computing area under the curve, "bayestestR" package
  library(papaja)       # APA conform output, "papaja" package
  library(lmerTest)     # for multilevel modeling
  library(afex)         # compute repeated measures ANOVA, "afex" package
  library(emmeans)      # for custom contrasts in ANOVAs, "emmeans" package
  library(sjPlot)       # plot MLM model fit
  library(kableExtra)   # for great tables in R Markdown
  library(interactions) # for simple slopes analysis
  library(huxtable)     # create huxtable
  library(glmmTMB)      # from the glmmTMB package for multi level models
  library(BayesFactor)  # computing Bayes factors, "BayesFactor" package
  library(ggplot2)      # for plotting, "ggplot2" package

@@

  sca_results <- data.frame(pipeline = character(), beta = double(), pvalue = double(), predictor = character())

  # loop through the pipelines

@@

    newdata <- data.frame(pipeline = c(names(pipelines_data[i]),names(pipelines_data[i])),
                          beta = c(summary(m1_sca)$coefficients[2,1],summary(m1_sca)$coefficients[3,1]),
                          pvalue = c(summary(m1_sca)$coefficients[2,5],summary(m1_sca)$coefficients[3,5]),
                          predictor = c("Level", "NFC"))
    sca_results <- rbind(sca_results, newdata)

@@

  # add a row number and sort the data frame by the fixed effects estimate of the predictor 'level'

  sca_results <- cbind(sca_results, num = rep(c(1:(nrow(sca_results)/2)), each = 2))
  sca_results <- sca_results[order(sca_results$predictor, sca_results$beta, decreasing = TRUE), ]
  sca_results[sca_results$predictor == "NFC", ] <- sca_results[match(sca_results$num[sca_results$predictor == "Level"],
                                                                     sca_results$num[sca_results$predictor == "NFC"]),]

  # lock it in place by turning it into a factor

  sca_results$num <- factor(sca_results$num, levels = sca_results$num[sca_results$predictor == "NFC"])

  # create the upper panel first, which will show the estimates of 'level' and 'nfc'

  sca_upperplot <- ggplot(data = sca_results, aes(x = num, y = beta, color = predictor, group = predictor)) +
    geom_point() +
    geom_line() +
    theme_classic() +
    labs(x = NULL, y = "Fixed effects estimate") +
    scale_y_continuous(position = "right") +
    theme(axis.text.x = element_blank())
